---
title: "My project"
author: "Aiden Liu"
output: html_document
---

```{r, include = FALSE}
here::i_am("Rmd/report.Rmd")
knitr::opts_knit$set(root.dir = here::here())
```


```{r}
setwd("..")
wine <- read.csv("./wine.csv")

```
1.data cleaning  
Since I get the data from a standrad data website, the data cleaning step won't take much work.
```{r}
which(is.na(wine))

```

2.some figures
```{r}
hist(wine[,2],
     main="Histogram of Volatile Acidity",
     xlab="volatile acidity",
     ylab="number",
     breaks=8 ,
     col ="yellow")
plot(x=wine$pH,
     y=wine$quality,
     xlab="pH",
     ylab="quality",
     col ="blue",
     main="scatters of pH and quality"
)
boxplot(wine$pH ~ wine$quality,
        main="Boxplots of pH by quality",
        xlab="quality",
        ylab="pH",
        col=c("red","orange","yellow","green","blue","purple"),
        names= c("3","4","5","6","7","8")
)
```
3.decription of analysis
According to the plots above, we can find there might be a negative correlation between the pH of a bottle of wine and its quality.

```{r}

ph <- lm(wine$pH ~ wine$quality, data = wine)
summary(ph)
```
After this step, it seems that there is a negative correlation within the two variables.  
However, we need further analysis to verify this conclusion.
Also we can find some basic statistical information of the data in the dataset.
```{r}
summary(wine)
```
Now,by fewer analysing on the data, we have a elementary understanding of our data and make our first step to the relations between the quality of a bottle of wine and its quality. 